Manuscript draft

### 2019-08-27 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

>>>>

Our results show that productivity decreases linearly with latitude. Climate explains a significant proportion of variation in all carbon fluxes, with temperature variables being the best predictors of productivity. While other climate variables are significant predictors of productivity, none of them improve on the explanatory power of temperature-related variables. Water availability is an important factor in explaining productivity on a global scale: we find a positive influence of precipitation at low MAP, with saturation at higher levels of MAP. There is a significant interaction between MAT and MAP.

We find that seasonality is an important factor in understanding patterns in productivity on a global scale: temperature seasonality and growing season length are strong predictors of productivity, though growing season length doesn't improve on MAT as a predictor. Within the growing season we find the influence of climate on productivity is smaller, but still significant for a number of carbon fluxes.
